\documentclass[10pta]{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{tfrupee}
\usepackage{fontawesome5}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Rikin Parekh} % Your name
\lastUpdated{March, 2026}

% You can merge both of these into a single line, if you do not have a website.
\address{
% +91 8320 33 8778 \\ 
Ahmedabad, Gujarat \\ \href{mailto:rikinparekh15147@gmail.com}{rikinparekh15147@gmail.com} \\ \href{https://linkedin.rikinparekh.in}{linkedin.rikinparekh.in}} 
\address{  }  

\begin{document}



%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------


\begin{rSection}{PROFILE}

{Embedded systems and robotics engineer skilled in digital systems, microcontrollers, and low-level programming. Built processor-level architectures at IIT Gandhinagar and end-to-end IoT systems using STM32, ESP, and Raspberry Pi. Recipient of \rupee 3.2L+ in government grants and national hackathon finalist.}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Technology in Information and Communication Technology},\\ Pandit Deendayal Energy University \hfill {Expected 2027}
\begin{list}{$\circ$}{}
    \item \textbf{CGPA:} 9.08/10.0  [upto 5\textsuperscript{th} Semester]
    \item \textbf{Coursework:} Embedded Systems, Digital Signal Processing and Communication, AI Systems, Data Structures and Algorithm, Computer Organisation and Design, 3D Modeling
\end{list}


{\bf HSC - 12th Grade}, Best Higher Secondary School \hfill {2023}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}



%-- experience %--
\begin{rSection}{Experience}

{\bf Electronics and Embedded Systems Engineer Intern}, \\
Center for Creative Learning, IIT Gandhinagar \href{https://rikinparekh.in/internship/ccl_iitgn_report.pdf}{\faFile} \hfill {July 2025 -- February 2026}
\begin{list}{$\circ$}{}
    \item Designed advanced digital-systems prototypes under Prof. Manish Jain for the India Semiconductor Mission, including a fully functional 8-bit breadboard computer; wrote low-level AVR assembly and custom drivers for ATmega328 and display modules.
    \item Demonstrated projects to national dignitaries including Hon. Shri S. Somnath, Union Ministers Pradhan \& Vaishnaw, and senior officials from NCERT, CBSE, NIC, and MoHA.
\end{list}

{\bf Embedded Systems Engineer Intern}, STEMbotix \hfill {May 2025 -- June 2025}
\begin{list}{$\circ$}{}
    \item Built a production-ready quadruped robot and an interactive STEM game system, developing firmware, peripheral interfaces, and hardware integration across STM32 and other microcontroller platforms.
\end{list}

\end{rSection}


\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Python, C, Embedded C, Assembly, MATLAB
\\
Microcontrollers and Platforms & AVR (Arduino), ESP32/ESP8266, ARM Cortex-M (STM32), Raspberry Pi \\
Frameworks and Tools & Microchip Studio, OpenCV, Django, Flask, Rest APIs, Solid Works,\\ & Datamatics TruBot, Git, Numpy, Pandas, Linux\\
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\textbf{Print\&Go – Smart Printing Kiosk}  \href{https://printandgo.co.in}{\faGlobe}
\hfill 2025 - Present\\
    \textit{Received \rupee2.5L grant under the Government of Gujarat’s Student Startup \& Innovation Policy (SSIP).}
    \begin{itemize}
    \item Designed a 24×7 self-service document-printing vending machine with peer-to-peer encryption, secure file upload, and automated payment/printing workflow.
\end{itemize}

\textbf{SegReClaim – Incentive-Based Waste Collection System} \href{https://segreclaim.rikinparekh.in}{\faGlobe} \hfill 2025 - Present\\
    \textit{Received \rupee70k grant under the Government of Gujarat’s Student Startup \& Innovation Policy (SSIP).}
     \begin{itemize}
    
    \item Built a reverse-vending IoT system that automatically identifies, segregates, and rewards recyclable waste deposits, promoting sustainable disposal practices.
\end{itemize}

\textbf{Underwater ROV} \hfill 2024\\
    \textit{Cleared Level I of Robofest and was awarded \rupee50,000 funding for continued development.}
 \begin{itemize}

    \item Developed ideation and a prototype for a remotely operated underwater vehicle (ROV) for submerged structural inspection, engineering a BLDC motor-driven propulsion system controlled via Raspberry Pi for real-time 6-DOF maneuvering; secured \rupee 50,000 in development funding upon advancing at Robofest, validating the design's technical and commercial potential.
% \item Designed and developed a remotely operated underwater vehicle for structural analysis of submerged infrastructure.

% \item Integrated BLDC motors with a Raspberry Pi for precise maneuverability and real-time control.
\end{itemize}

\textbf{8 bit CPU on breadboard from scratch} \hfill 2025
 \begin{itemize}
    \item \textbf{Engineered a fully functional 8-bit CPU from scratch on a breadboard}, implementing a custom programmable control unit using EEPROM as a lookup-based instruction decoder, a Python-scripted binary ROM generator, and an 8×8-bit RAM architecture using 74LS189 ICs — demonstrating deep understanding of digital logic and computer architecture at the hardware level.
    \item \textbf{Designed and executed a complete instruction execution pipeline} featuring a 8-bit program counter (with 74LS161) with JMP and branch support, a variable-frequency clock module (555 timer) with manual/auto switching, and successfully validated the system by running the Fibonacci series — proving end-to-end functionality from clock signal to program output.
\end{itemize}

% \textbf{Robotic Process Automation}  \href{https://github.com/Jayesh-Gautam/Datamatics-Hackathon}{\faGithub} \hfill 2024\\
% \textit{Reached the finals of the Datamatics Hackathon at IIT Bombay}
%  \begin{itemize}
%     \item Developed an RPA solution using Python and Datamatics automation frameworks to streamline data extraction and processing; selected as a finalist at IIT Bombay.
%    % \item
%    %  Developed an \textbf{RPA} solution at the \textbf{Datamatics Hackathon} to automate repetitive business processes, enhancing efficiency and accuracy. 
%    %  \item Designed and implemented a bot using \textbf{Python and Datamatics automation frameworks} to streamline data extraction, processing, and reporting. 
%    %  \item Successfully reached the finals at \textbf{IIT Bombay}, showcasing the solution’s impact and scalability in real-world applications.
%  \end{itemize}
 
%  \textbf{Smart Mirror} \hfill 2023\\
%     \textit{Showcased at National Children’s Science Congress (NCSC) 2023}
%  \begin{itemize}

%     \item Developed a Raspberry Pi–powered smart mirror displaying daily routines, calendars, news, and media controls using a two-way reflective film and modular UI.
%  % \item
%  %    Developed a smart mirror that displays \textbf{daily routines}, Google Calendar events, and New York Times news, while also allowing Spotify control and \textbf{integration with smart assistants} like Google Assistant or Alexa. Powered by a \textbf{Raspberry Pi}, it uses a \textbf{two-way film} on the surface, enabling it to function as both a display and a regular mirror, creating an interactive and functional addition to any smart home.
%     %  \item Achieved X\% growth for XYZ using A, B, and C skills.
%     %  \item Led XYZ which led to X\% of improvement in ABC
%     % \item Developed XYZ that did A, B, and C using X, Y, and Z. 
%  \end{itemize}
 
 
% \textbf{Indian AI Product Finder} \hfill 2021\
%  \begin{itemize}

% \item Applied natural language processing (NLP) techniques to analyze customer descriptions.

% \item Designed the system to recommend local Indian alternatives based on user queries. Utilized a Kaggle-sourced Amazon dataset containing Indian products.
%  \end{itemize}
 


 % \textbf{Computer Vision for Waste Segregation using MobileNet Architecture} \hfill 2025\
 % \begin{itemize}
 % % \item[]
 %    \item 
 %    Implemented a waste classification system using transfer learning on a pretrained MobileNet model.

 %    \item Fine-tuned the network to classify different types of waste materials (e.g., plastic, metal, organic).

 % \end{itemize}


\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{PROJECTS}
% \vspace{-1.25em}
% \item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
% \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
% \item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
% \end{rSection} 

%----------------------------------------------------------------------------------------
% % \begin{rSection}{Extra-Curricular Activities} 
% % \begin{itemize}
% %     \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
% %     \item	Sample bullet point.
% % \end{itemize}


% \end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
    \item \textbf{Top 5 Finalist – Nirman 1.0, PDEU SOM \& IIC } \hfill Apr, 2025 \\ Secured 5th position in a university-level innovation and entrepreneurship competition. Received a cash prize of \rupee8000. Project details are confidential due to ongoing development potential.
    \item \textbf{Two Time Finalist - Datamatics Hackathon, IIT Bombay } \hfill Dec, 2024\\ \hspace*{\fill} Dec, 2023 \\ Developed an RPA solution to automate business processes, enhancing efficiency and accuracy.
    \item \textbf{Winner - Round 1, Robofest (Underwater ROV Category)}  \hfill Aug, 2024 \\ Led a team in designing and prototyping a remotely operated underwater vehicle for structural analysis of submerged infrastructure. Secured \rupee50,000 in funding.
    %     \item \textbf{Exhibitor - National Children's Science Congress (NCSC) \& Tarang Fest } \hfill Jan, 2023 \\ Presented smart mirror and IoT-based projects representing Atal Tinkering Lab.
\end{itemize}
\end{rSection}

\begin{rSection}{Co-Curricular Experience}
\begin{itemize}
    \item \textbf{Cretus Robotics Club - Technical Lead} \\ Engaged in hands-on robotics workshops, hackathons, and technical competitions, expanding expertise in embedded systems, automation, and AI.  
    % \item \textbf{Intel AI Bootcamp - Participant} \\ Developed an AI-based Indian product finder for Amazon, leveraging machine learning techniques to enhance search optimization.  
    \item \textbf{Atal Tinkering Lab - Mentor \& Workshop Conductor} \\ Supervised and organized STEM workshops for students, promoting innovation in robotics and IoT.    
\end{itemize}
\end{rSection}

\begin{rSection}{Certifications \& Learning} 
\begin{itemize}
    \item \textbf{Silver Elite Certification – Drone Systems \& Control (IISc Bangalore, Score: 83\%) } \href{https://archive.nptel.ac.in/noc/Ecertificate/?q=NPTEL25AE30S115060018110775085}{\faFile}
\hfill 2025
    \item \textbf{IBM SkillsBuild: Building AI Solutions Using Advanced Algorithms and Open Source Frameworks } \href{https://www.credly.com/badges/97f94498-22fa-4daa-8b79-af7fa23581db/}{\faFile} \hfill 2025
\item \textbf{Hosted Robotics \& Embedded Systems Workshop at New LJ university} \href{https://rikinparekh.in/resume/lj_host_cert.pdf}{\faFile} \hfill 2026
    % \\ Learned to build AI models using advanced machine learning algorithms and open-source frameworks such as scikit-learn.
    % \item \textbf{Harvard CS50: Introduction To AI} \hfill2024 \\Covers fundamental AI concepts, machine learning, and neural networks 
    % \item \textbf{Intel AI Bootcamp }\hfill 2021
    % \\Focused on NLP, trained an AI-based Indian product finder using Amazon product datasets.
\end{itemize}


\end{rSection}


\end{document}
